---
# Preamble
title: \huge \textsc{Test Document}
subtitle: \textit{a small sample of \textbf{R Markdown}}

author: Kelly G. Roberts
date: \today

bibliography: ./uni.bib

header-includes:
  \pagenumbering{gobble}
  \usepackage{appendix}
  \usepackage{booktabs}
  \usepackage{indentfirst}
  \usepackage{lipsum}
  \usepackage{pdfpages}
  \usepackage{titling}
    \renewcommand\maketitlehooka{\null\mbox{}\vfill}
    \renewcommand\maketitlehookd{\vfill\null}

output:
  pdf_document:
    latex_engine: xelatex
    highlight: zenburn
    number_sections: yes

# thanks: To my sister, Banana. Love ya, Nans.
---

<!-- some extra junk to make the title page, toc, and numbering show up the way I want -->
\newpage
\pagenumbering{arabic}
\tableofcontents
\newpage



\abstract{Showing various ways that R Markdown allows for combining statistical analysis and LaTeX
code into a cohesive whole.}



# Overview
So, let's talk about this whole \LaTeX{} thing, shall we?

## On the Subject of \LaTeX
This article serves as a brief overview of the \LaTeX{} document preparation
system coupled with examples of the complex formatting it can help achieve. It
must be emphasized that this is only a basic guide to help familiarize you with
the power of using \LaTeX{} as a means to prepare professional-level
documentation.

### Okay... so what can I, like, *do* with it?
Honestly? Whatever you want! You can do basically everything you could ever need
to do when it comes to formatting a document in a professional and consistent way.
This is one of the key benefits of using \LaTeX{}; as long as you give the appropriate
commands and syntax, your document will appear exactly as you specified. This is
especially true when it comes to formatting items like equations. Have you ever
tried to write a mathematical formula in something like Word? It can be an absolute
nightmare to get the formatting correct without destroying the other text in the
document.

\
\indent Here's an example of a continued fraction, something that would be
\emph{exceptionally} difficult to write out in Word:

$$ e=2+\frac{1}{1+\frac{1}{2+\frac{2}{3+\frac{3}{4+\frac{4}{5+\ddots}}}}} $$

\
\indent Now, that may look like it would be complicated to input into your text editor,
but I can assure you that \LaTeX{} makes this quite easy; all it takes is
learning some basic commands.



# Examples

> "I will, in fact, claim that the difference between a bad programmer and a good one is whether he considers his code or his data structures more important.
> Bad programmers worry about the code.
> Good programmers worry about data structures and their relationships."
>
> `r tufte::quote_footer('--- Linus Torvalds')`

\
\indent This time we actually used another package that we grabbed within our root *R* environment (`sudo R`) followed by the subcommand `install.packages('tufte')`. It allows us to put neat little footers into our block quotes. Neat, huh?

\
\indent As stated by @aissen99, blah blah blah words words words. As you can see,
all of the information that will end up in our bibliography is here, including the
names of editors, the publisher, and the year of publication. Using this format,
we can now call our new entry by its name, which in this case is `@aissen99`. Names
can be whatever you choose that is easy to remember for you. I chose to use the
author's last name and the year of publication.

## Look at this table
|Model             |MPG  |Cyl |Disp|HP  |
|:-----------------|----:|---:|---:|---:|
|Mazda RX4         |21.0 |6   |160 |110 |
|Mazda RX4 Wag     |21.0 |6   |160 |110 |
|Datsun 710        |22.8 |4   |108 |93  |
|Hornet 4 Drive    |21.4 |6   |258 |110 |
|Hornet Sportabout |18.7 |8   |360 |175 |
|Valiant           |18.1 |6   |225 |105 |

## Lists: Nature's Organizer
1. First
    * subfirst
    * submore
    * subagain
1. Second
    * subsecond
        * deeper
            * still
    * subsecondsecond
1. Third



# How about that **R**, though?

\
Here's something cool that you can do with code blocks: evaluate R code.

```{r}
2+2
```

\
In this case, we evaluated the chunk `2+2` into the output shown above.

\
How about some more complicated equations?

```{r}
5*40
```

```{r}
3^9
```

```{r}
values <- rnorm(5)
values
```

\newpage



# References
