---
title: \huge \textsc{Test Document}
subtitle: \textit{a small sample of \textbf{R Markdown}}
author: Kelly G. Roberts \textit{(kgr)}
bibliography: ./uni.bib
date: \today
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{pdfpages}
- \usepackage{titling}
    \renewcommand\maketitlehooka{\null\mbox{}\vfill}
    \renewcommand\maketitlehookd{\vfill\null}
- \usepackage{lipsum}
- \usepackage{appendix}
- \pagenumbering{gobble}
---
\newpage
\pagenumbering{arabic}
\tableofcontents
\newpage

# Overview
\section{Introduction}

This article serves as a brief overview of the \LaTeX{} document preparation
system coupled with examples of the complex formatting it can help achieve. It
must be emphasized that this is only a basic guide to help familiarize you with
the power of using \LaTeX{} as a means to prepare professional-level
documentation.

\section{On the Subject of \LaTeX}

\subsection{Okay... so what can I, like, \textit{do} with it?}

Honestly? Whatever you want!

You can do basically everything you could ever need to do when it comes to
formatting a document in a professional and consistent way. This is one of the
key benefits of using \LaTeX{}; as long as you give the appropriate commands and
syntax, your document will appear exactly as you specified. This is especially
true when it comes to formatting items like equations. Have you ever tried to
write a mathematical formula in something like Word? It can be an absolute
nightmare to get the formatting correct without destroying the other text in the
document.

Here's an example of a continued fraction, something that would be
\emph{exceptionally} difficult to write out in Word:

$$ e=2+\frac{1}{1+\frac{1}{2+\frac{2}{3+\frac{3}{4+\frac{4}{5+\ddots}}}}} $$

Now, that may look like it would be complicated to input into your text editor,
but I can assure you that \LaTeX{} makes this quite easy; all it takes is
learning some basic commands.

\section{Examples}

Here's where some examples would be...

IF I HAD THEM.

Oh wait... I *do* have some. How about block quotes?

> "If it weren't for my lawyer, I'd still be in prison.
>  It went a lot faster with two people digging."
>
> `r tufte::quote_footer('--- Joe Martin')`

> "I will, in fact, claim that the difference between a bad programmer and a good one is whether he considers his code or his data structures more important.
> Bad programmers worry about the code.
> Good programmers worry about data structures and their relationships."
>
> `r tufte::quote_footer('--- Linus Torvalds')`

This time we actually used another package that we grabbed within our root *R* environment (`sudo R`) followed by the subcommand `install.packages('tufte')`. It allows us to put neat little footers into our block quotes. Neat, huh?

\section{Citing a Bibliography or Reference Document}

As you can see, all of the information that will end up in our bibliography is
here, including the names of editors, the publisher, and the year of
publication. Using this format, we can now call our new entry by its name,
which in this case is `@aissen99`. Names can be whatever you
choose that is easy to remember for you. I chose to use the author's last name
and the year of publication.

# Look at this table
|Model             |MPG  |Cyl |Disp|HP  |
|:-----------------|----:|---:|---:|---:|
|Mazda RX4         |21.0 |6   |160 |110 |
|Mazda RX4 Wag     |21.0 |6   |160 |110 |
|Datsun 710        |22.8 |4   |108 |93  |
|Hornet 4 Drive    |21.4 |6   |258 |110 |
|Hornet Sportabout |18.7 |8   |360 |175 |
|Valiant           |18.1 |6   |225 |105 |

## Lists: Nature's Organizer
Boy howdy, that sure is a subsection.

0. Look
0. at
0. this
0. list
0. isn't
0. it
0. neat

* unordered
* this
* time

# Section 2: Electric Boogaloo
Oh look, some more text.

Very nice.

Remember that table from earlier? Here's a neat code block:

```
|Model             |MPG  |Cyl |Disp|HP  |
|:-----------------|----:|---:|---:|---:|
|Mazda RX4         |21.0 |6   |160 |110 |
|Mazda RX4 Wag     |21.0 |6   |160 |110 |
|Datsun 710        |22.8 |4   |108 |93  |
|Hornet 4 Drive    |21.4 |6   |258 |110 |
|Hornet Sportabout |18.7 |8   |360 |175 |
|Valiant           |18.1 |6   |225 |105 |
|Sample            |19.0 |3   |256 |420 |
```

That's exactly how it looked in this `.rmd` file.

Pretty fuckin' wild, eh?

## How about that **R**, though?
Is it neat? Yes!

Here's something cool that you can do with code blocks: evaluate R code.

```{r}
2+2
```
In this case, we evaluated the chunk `2+2` into the output shown above.

How about some more complicated equations?

```{r}
5*40
```

```{r}
3^9
```

```{r}
values <- rnorm(5)
values
```

Wow, we evaluated the *shit* out of those expressions.

## More Lists
Perhaps another list?

1. First
    * subfirst
    * submore
    * subagain
1. Second
    * subsecond
        * deeper
            * still
    * subsecondsecond
1. Third

As stated by @aissen99, blah blah blah words words words.

\newpage

# References
